Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
Added crosslinking results

\section*{Results and Discussion}

In order to construct an initial configuration which gives reliable 
trends, we need to understand the composition of layers, how far apart
to stack the layers, and how to orient them with respect to each other.
To verify our choices for each parameter, we compare our calculations
to experimental small angle X-ray scattering (SAXS), wide angle X-ray
scattering (WAXS), and ionic conductivity measurements.

@@

The model gives reasonable estimates of ionic conductivity for both phases.
Calculated values of ionic conductivity obtained using the Nernst Einstein
relation and Collective Diffusion model are compared in Table~\ref{table:conductivity}.
The two methods agree with each other within error, although the 
uncertainty obtained using the Collective Diffusion model is much higher.
Much longer simulations are needed to lower the uncertainty.
For this reason we will likely only use the Nernst Einstein relation
in future calculations of this type. Interestingly, Basin B 
has a higher ionic conductivity than Basin A. Conductivity is enhanced in
Basin B due to a higher sodium ion diffusivity. Transport of sodium is
likely facilitated by the homgeneity of Basin B. Sodium ions have less
sites to move to in Basin A. In all cases, our calculated values
are higher than experimental values, as expected. Some of the 
discrepancy is likely a result of using an imperfect forcefield. However, the real system, 
although mostly aligned and straight, has a distribution of 
azimuthal angles. This means that the pores have a degree of tortuosity 
which lowers the effective ionic conductivity of the bulk 
membrane. The ordering from isotropic to mostly aligned mesophases 
showed an 85 fold increase in ionic conductivity. We would expect additional
gains in a perfect system.

\begin{table}
\centering
\begin{tabular}{ccc}
\toprule
\multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
\hline
Method & Basin A & Basin B \\
\midrule
Nernst Einstein & \num{(1.23$\pm$0.01)e-4} & \num{(1.76$\pm$0.02)e-4} \\
Collective Diffusion & \num{(1.40$\pm$0.32)e-4} & \num{(4.6$\pm$2.4)e-4} \\
Experiment & \num{(1.33$\pm$ 0.10)e-5} & -- \\
\bottomrule
\end{tabular}
\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
agree within error. Both methods give calculated values of ionic conductivity which
are an order of magnitude higher than experimental values~\label{table:conductivity}}
%MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
	\end{table}

>>>>

\section*{Results and Discussion}
\subsection*{Determination of system structural details}
In order to construct an initial configuration which gives reliable 
trends, we need to understand the composition of layers, how far apart
to stack the layers, and how to orient them with respect to each other.
To verify our choices for each parameter, we compare our calculations
to experimental small angle X-ray scattering (SAXS), wide angle X-ray
scattering (WAXS), and ionic conductivity measurements.

@@

\subsection{Ionic conductivity calculation}

The model gives reasonable estimates of ionic conductivity for both phases.
Calculated values of ionic conductivity obtained using the Nernst Einstein
relation and Collective Diffusion model are compared in Table~\ref{table:conductivity}.
The two methods agree with each other within error, although the 
uncertainty obtained using the Collective Diffusion model is much higher.
Much longer simulations are needed to lower the uncertainty.
For this reason we will likely only use the Nernst Einstein relation
in future calculations of this type. Interestingly, Basin B 
has a higher ionic conductivity than Basin A. Conductivity is enhanced in
Basin B due to a higher sodium ion diffusivity. Transport of sodium is
likely facilitated by the homgeneity of Basin B. Sodium ions have less
sites to move to in Basin A. Currently there is no experimental
evidence of this trend, but it may be the subject of a future study. 
In both cases, our calculated values for Basin A are higher than the 
experimental values, as expected. Some of the discrepancy is likely a result
of using an imperfect forcefield. However, the real system, although mostly
aligned and straight, has a distribution of azimuthal angles, meaning 
that the pores have a degree of tortuosity which lowers the effective 
ionic conductivity of the bulk membrane. The ordering from isotropic to
mostly aligned mesophases showed an 85 fold increase in ionic conductivity.
We would expect additional gains in a perfect system.

\begin{table}
\centering
\begin{tabular}{ccc}
\toprule
\multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
\hline
Method & Basin A & Basin B \\
\midrule
Nernst Einstein & \num{(1.23$\pm$0.01)e-4} & \num{(1.76$\pm$0.02)e-4} \\
Collective Diffusion & \num{(1.40$\pm$0.32)e-4} & \num{(4.6$\pm$2.4)e-4} \\
Experiment & \num{(1.33$\pm$ 0.10)e-5} & -- \\
\bottomrule
\end{tabular}
\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
agree within error. Both methods give calculated values of ionic conductivity which
are an order of magnitude higher than experimental values~\label{table:conductivity}}.
\end{table}

\subsection{Implementation of the crosslinking algorithm}

We applied the crosslinking algorithm to an equilibrated structure in Basin B.
The procedure will be repeated with Basin A in the near future.
The resulting crosslinked structure has an even distribution of
crosslinks between monomer tails of the same monomer, monomers stacked on  % table of values here
top of each other and monomers in other pores, including across periodic
boundaries. The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
constant under a range of simulation conditions. Figure~\ref{fig:xlink} compares
the pore behavior of a system that was a crosslinked and simulated for 10 ns to 
the pore behavior of the same system taken just before crosslinking and run for 10 ns.
Rather than plotting an average pore spacing, each pore-to-pore distance is plotted
separately. Visually, one can tell that the crosslinked pores are locked in place. 
The smaller pore spacing is also apparent by comparing the two plots. 
The simulations discussed previously have not been crosslinked. Moving forward,
the sandwiched system will be crosslinked in Basin A and used for
transport studies.

\begin{figure}
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.png}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
\end{figure}
